How do changes in ex vary between countries?

### 2022-03-09 draft_paper.Rmd
Added a table! Eventually.

compare_best_breakmodel_with_null %>% 
  mutate(
    aic_alt  = map_dbl(model_alt, AIC),
    aic_null = map_dbl(model_null, AIC)
  ) %>% 
  mutate(
    alt_preferred = map2_lgl(aic_alt, aic_null, ~ifelse(.x < .y, TRUE, FALSE))
  )

@@

>>>>

tmp <- compare_best_breakmodel_with_null %>% 
  mutate(
    aic_alt  = map_dbl(model_alt, AIC),
    aic_null = map_dbl(model_null, AIC)
  ) %>% 
  mutate(
    alt_preferred = map2_lgl(aic_alt, aic_null, ~ifelse(.x < .y, TRUE, FALSE))
  ) %>% 
  mutate(
    anova_results = map2(model_alt, model_null, anova)
  ) %>% 
  mutate(
    ftest_pval = map_dbl(anova_results, ~.[2,6]),
    stat_sig_preference = ftest_pval < 0.05
  )

@@

Next, we display a table with those countries where the breakpoint shows as statistically significant compared to the null, where best_tau is the year.

```{r}
stat_sig_table <- select(tmp, code, x, sex, best_tau, stat_sig_preference) %>% filter(stat_sig_preference==TRUE)

rename(stat_sig_table, age = x, country = code)
view(stat_sig_table)

#using flextable
myft <- flextable(stat_sig_table)
myft
myft <- theme_vanilla(myft)
myft
```
